Combining information from photometric and spectroscopic data:\\ Don't waste your time in spectrophotometric calibration!

### 2014-05-16 tex/ms.tex
updating model description for nebular lines

\section{Experiments and results}

@@

\subsection{Data}
BDJ/DRW WORDS ABOUT DATA

\subsection{Star Cluster Model}
We model the stellar cluster as a single age SSP. The spectrum of a
star cluster under this assumption is given by
\begin{eqnarray}\displaystyle\label{eq:MeanModel} 
\mu(\theta, \lambda_o) & = &
\frac{m_*}{4\pi d_L^2(1+z)} \, G(\lambda,\sigma_v) \otimes 
S(\lambda, t, Z [, \beta]) \, e^ {-k_\lambda\tau_V} 
\\ 
\lambda_o & = & (1+z)\,\lambda 
\\
\theta & \equiv & \left[ m_*, t, Z, \tau_V, \sigma_v, z, d_L, \beta \right]
\quad ,
\end{eqnarray} where the parameters $\theta$ include the stellar mass
$m_*$, effective optical depth to dust in the $V$-band $\tau_V$,
velocity dispersion $\sigma_v$, luminosity distance $d_L$, and
redshift $z$.  The spectrum of one solar mass of stars that formed at
lookback time $t$ with metallicity $Z$ is given by $S(\lambda, t, Z [,
\beta])$ where the additional parameters $\beta$ may include details
of the population synthesis model, such as the IMF slope and
adjustments to the stellar spectra or stellar evolutionary tracks
\citep[e.g.][]{FSPS}. We will assume $\beta$ to be fixed for the
purposes of this exercise, with no loss of generality (KEEPING IMF
SLOPE CONSTANT FOR NOW).  We will also fix the shape of the
attenuation curve, $k_\lambda \equiv \tau_\lambda/\tau_V$ to the Milky
way average of \citet{CCM89} with $R_V=3.1$ and assume that $d_L$ is
known to high precision from independent methods. (BDJ NOTE TO SELF -
do not use $k$ for the attenuation curve shape - will confuse people
used to reddening curves.  Even though it's super handy.)

@@

We calculate $S(\lambda, t, Z)$ using the Flexible Stellar Population
Synthesis code \citep[FSPS][]{FSPS}.  We use the Padova isochrones
\citep{Padova} and high-resolution theoretical stellar spectra
\citep{CKC14} which allow us to probe super-solar metallicities at
early ages.  NEBULAR EMISSION - MASK OR INFER?  The model spectra are
smoothed by convolution with a Gaussian in velocity space, and are
interpolated to the wavelength points of the of the observed spectrum
taking into account the redshift.

\subsection{Sampling and Priors}
We estimate the posterior through MCMC sampling. Our sampling of the
posterior is accomplished using \texttt{emcee} \cite{dfm} after an
intial round of optimization using Powell's method.  \texttt{emcee} is
an implementation of the affine-invariant ensemble sampler of
\citet{GW}, and unlike typical Metropolis-Hastings MCMC sampling does
not require the specification of step sizes in each dimension.  Our
prior distributions are in all cases top-hat functions, though more
informative priors distributions may be used.  Informative priors may
be especially appropriate for the calibration parameters $\alpha$ if
additional information about the instrument is available or for the
parameters of interest $\theta$, for example in the case where there
is knowledge of the metallicity distribution of the population from
which a given cluster is drawn.

@@

In Figure \ref{fig:calibrated_triangle} we show the marginalized and
joint-pdfs for the parameters.

@@

BDJ INSERT WORDS HERE.
BDJ random issues, collected here in case we want to address them and
to keep me from cluttering up the main text: effective aperture
corrections (i.e. we're implicitly assuming photometry and
spectroscopy sample the same population).  Sky subtraction residuals.
Model resolution and instrument resolution.  Method only useful when
you have a model for the mean spectrum?  How to interpret GP
residuals, as a fn of S/N?  Photometric upper limits? Infer the
wavelength solution as well - stellar population (and telluric lines) as your arc.

>>>>

\section{Experiments and Results}

@@

\subsection{Test Data}
The data we use to test our method consists of MMT Hectospec
spectroscopy of XX stellar clusters in M31 for which YY-band HST
photometric data exist.  The optical spectra were obtained by
\citet{caldwell}.  The wavelength range of the spectra is $3700-7200
\AA$. The instrumental resolution is $\sim 5\AA$ across the optical
range \citep{fabricant13}.  Sky subtraction happened.  We got data
which were uncalibrated and data which had been approximately
spectrophotometrically calibrated using an average for the night (MORE
HERE).

DRW/BDJ WORDS ABOUT DATA

\subsection{Star Cluster Model}
We model the stellar cluster as a single age SSP. The spectrum of a
star cluster under this assumption is given by
\begin{eqnarray}\displaystyle\label{eq:MeanModel} 
\mu(\theta, \lambda_o) & = &
\frac{m_*}{4\pi d_L^2(1+z)} \, G(\lambda,\sigma) \otimes 
S(\lambda, t, Z [, \beta]) \, e^ {-k_\lambda\tau_V}  +
\sum_{i=0}^{N_l} \frac{a_i}{\sigma_e\sqrt(2\pi)} e^{-(\lambda - \lambda_i)^2/(2\sigma_e^2)}
\\ 
\lambda_o & = & (1+z)\,\lambda 
\\
\theta & \equiv & \left[ m_*, t, Z, \tau_V, \sigma_v, z, d_L, \beta,
  \{a_i\}_{i=0}^{N_l}, \sigma_n \right]
\quad ,
\end{eqnarray} where the parameters $\theta$ include 
the stellar mass $m_*$, 
effective optical depth to dust in the $V$-band $\tau_V$,
velocity dispersion or instrumental resolution $\sigma$, 
luminosity distance $d_L$, 
and redshift $z$.  
The spectrum of one solar mass of stars that formed at lookback time
$t$ with metallicity $Z$ is given by $S(\lambda, t, Z [, \beta])$
where the additional parameters $\beta$ may include details of the
population synthesis model, such as the IMF slope and adjustments to
the stellar spectra or stellar evolutionary tracks
\citep[e.g.][]{FSPS}. We will assume $\beta$ to be fixed for the
purposes of this exercise, with no loss of generality (KEEPING IMF
SLOPE CONSTANT FOR NOW).  We will also fix the shape of the
attenuation curve, $k_\lambda \equiv \tau_\lambda/\tau_V$ to the Milky
way average of \citet{CCM89} with $R_V=3.1$ and assume that $d_L$ is
known to high precision from independent methods.

Nebular emission lines (which may arise from HII regions around the
clusters or from a diffuse ionized gas) and interstellar absorption is
modeled as a sum of Gaussians of unknown amplitude $a_i$, all of the
same width $\sigma_e$ (which need not be the same as stellar
broadening $\sigma$) and with known central wavelengths $\lambda_i$.
For emission lines the amplitudes are constrained to be positive,
while for interstellar absorption (e.g. Na D and Ca K) the amplitudes
are constrained to be negative. This framework can be easily extended
to include more complex models for the nebular emission, such as
allowing line dependent widths.

@@

We calculate $S(\lambda, t, Z)$ using the Flexible Stellar Population
Synthesis code \citep[FSPS][]{FSPS}.  We use the Padova isochrones
\citep{Padova} and the MILES stellar spectral library.  The model
spectra are smoothed by convolution with a Gaussian in wavelength
space (to model the MMT line-spread function) and are interpolated to
the wavelength points of the of the observed spectrum while taking
into account the redshift.

\subsection{Sampling and Priors}

We estimate the posterior through MCMC sampling. Our sampling of the
posterior is accomplished using \texttt{emcee} \cite{dfm} after an
intial round of optimization using Powell's method.  \texttt{emcee} is
an implementation of the affine-invariant ensemble sampler of
\citet{GW}, and unlike typical Metropolis-Hastings MCMC sampling does
not require the specification of step sizes in each dimension.

Our prior distributions are in all cases top-hat functions, though
more informative prior distributions may be used.  Informative priors
may be especially appropriate for the calibration parameters $\alpha$
if additional information about the instrument is available or for the
parameters of interest $\theta$, for example in the case where there
is knowledge of the metallicity distribution of the population from
which a given cluster is drawn.

\subsection{Results}

@@

In Figure \ref{fig:calibrated_triangle} we show the marginalized and
joint PDFs for the parameters.

Apparently we get really nice redshift/velocity constraints.

@@

BDJ INSERT WORDS HERE.
BDJ random issues, collected here in case we want to address them and
to keep me from cluttering up the main text: effective aperture
corrections (i.e. we're implicitly assuming photometry and
spectroscopy sample the same population).  Sky subtraction residuals.
Model resolution and instrument resolution.  Method only useful when
you have a model for the mean spectrum?  How to interpret GP
residuals, as a fn of S/N?  Photometric upper limits? Infer the
wavelength solution as well - stellar population (and telluric lines)
as your arc. Combinations of broadening in velocity space (physical)
and in wavelength space (instrumental)
